\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-12 evaluation.tex

We compared the bug-finding effectiveness of \psharp systematic concurrency testing to traditional ``stress testing'' without systematic concurrency control on several benchmark bugs, described below.  We report the length of time it took for the test to fail and remark on the effort needed to diagnose the bug from the test output. \MMComment{Overview of actual results?}

@@

Because we fixed all bugs that we discovered using the \psharp systematic testing engine in the case studies, for the evaluation we added an option to conditionally reintroduce each one of the bugs so that we can measure how fast and how often each bug can be discovered with the \psharp random and the PCT scheduler.

@@

>>>>

After we fixed all the bugs we could find in the programs under test, we added options to the code to introduce various benchmark bugs (some that were actually in the original programs and some we made up) one at a time so we could evaluate different methods to detect and diagnose them.  We compare \psharp systematic concurrency testing to traditional ``stress testing'' without systematic concurrency control; we report the average length of time it took for the test to fail and remark on the effort needed to diagnose the bug from the test output. \MMComment{Overview of actual results?}

@@

@@

For MigratingTable, the upper section of the table uses the random input generator described in Section~\ref{sec:mtable:input}.  For each bug that led to at least one test failure, we manually reviewed one of the failure traces to confirm it reflected the intended bug.  For each of the remaining bugs, we repeated the test using a test case custom written to trigger that particular bug in order to confirm that the failure to detect the bug in the original test was due to unlucky random choices of inputs and schedules and not some other problem with the experimental setup.  These results are in the lower section of the table; they can serve as additional cases in which to compare the random and PCT schedulers but do not represent a testing method one could use to find unknown bugs in software.  It may have been interesting to report results for specific test cases written before we knew the bugs as mentioned in \ref{sec:mtable:input}, but we did not do so in this study.

### 2015-09-12 experience.tex

>>>>

% It might be nice to include excerpts of a trace like in migration-bug3-explanation.pptx.  Unfortunately, the trace in migration-bug3-explanation.pptx doesn't match my recollection of the original diagnosis, which I want to write about truthfully (the former looks like it involves a stale streaming read, while I'm fairly sure the latter involved only the $k_O < k < k_N$ case).  If it's important, I could try to get a new trace consistent with the original diagnosis. ~ Matt
This bug took us only about 10 minutes to diagnose from the trace; granted, this is after we had days of experience analyzing MigratingTable traces and had added our own trace output to the test harness, since \psharp's built-in trace output is too low-level and does not include event payloads and other diagnostic data that is not passed between machines.  We started from the failure symptom: the virtual stream returned end-of-stream when according to the reference SpecTable, it should have returned an additional row with key 4.  We filtered the trace for actions by the same service machine and saw that $s_O$ was closed before the virtual stream had returned the row with key 4, but $s_N$ had already advanced past key 4 before the migrator inserted the row in the new table.  At first we found this phenomenon hard to believe, but soon we were convinced it reflected a gap in our design.
